---
title: "PSDistr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PSDistr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# PSDistr - Distributions Derived from Normal Distribution
**author: Piotr Sulewski, Pomeranian University**

<!-- badges: start -->
<!-- badges: end -->

Distributions derived from normal distribution are: two-piece power normal (TPPN), plasticizing component (PC), DS normal (DSN), expnormal (EN), 
Sulewski plasticizing component (SPC), easily changeable kurtosis (ECK) distributions. Density, distribution function, quantile function and random generation are presented.
To read more about the package please see (and cite :)) papers:

1) Sulewski P. (2021) DS Normal Distribution: properties and applications,
Lobachevskii Journal of Mathematics, 42(12), 2980-2999.
2) Sulewski P. (2022) Easily Changeable Kurtosis Distribution. Austrian Journal of Statistics, 52, 1-24.
3) Sulewski , P. (2022). New Members of The Johnson Family of Probability Distributions:
Properties and Application, Accepted: February 2022. REVSTAT-Statistical Journal.
4) Sulewski P. (2020) Normal Distribution with Plasticizing Component, Communications in Statistics ? Theory and Method, 51(11), 3806-3835.
5) Sulewski P., Volodin A. (2022) Sulewski Plasticizing Component Distribution: properties and applications. Lobachtetavskii Journal of Mathtetamatics, 43(8), 2286-2300.
6) Sulewski P. (2021) Two-Piece Power Normal Distribution, Communications in Statistics ? Theory and Method, 50(11), 2619-2639.

## Installation

You can install the released version of **PSDistr** from CRAN with:

``` r
install.packages("PSDistr")
```

You can install the development version of **PSDistr** from [GitHub](https://github.com/) with:

```r
library("remotes")
install_github("PiotrSule/PSDistr")
```

### Functions
  
**ddsn, pdsn, qdsn, rdsn**
  
Density, distribution function, quantile function and random generation for the DS Normal Distribution are calculated

```{r}
library(PSDistr)
ddsn(-0.5,2,2,2,0)
pdsn(-0.5,2,2,2,0)
qdsn(0.5,2,2,2,0)
rdsn(10,2,2,2,0)
```

**deck, peck, qeck, reck**
  
Density, distribution function, quantile function and random generation for the Easily Changeable Kurtosis Distribution are calculated

```{r}
deck(1,2,3)
peck(1,2,3)
qeck(0.5,2,3)
reck(10,2,3)
```

**den, pen, qen, ren**
  
Density, distribution function, quantile function and random generation for the Expnormal Distribution are calculated

```{r}
den(1,1,2,2,2,1)
pen(1,1,2,2,2,1)
qen(0.5,1,2,2,2,1)
ren(10,1,2,2,2,1)
```

**dpc, ppc, qpc, rpc**
  
Density, distribution function, quantile function and random generation for the Plasticizing Component are calculated

```{r}
dpc(0,1,2,2)
ppc(0,1,2,2)
qpc(0.5,1,2,2)
rpc(10,1,2,2)
```

**dspc, pspc, qspc, rspc**
  
Density, distribution function, quantile function and random generation for the Sulewski Plasticizing Component Distribution are calculated

```{r}
dspc(0,1,1,1,1,0)
pspc(0,1,1,1,1,0)
qspc(0.5,1,1,1,1,0)
rspc(10,1,1,1,1,0)
```

**dspc, pspc, qspc, rspc**
  
Density, distribution function, quantile function and random generation for the Two-piece Power Normal distribution are calculated

```{r}
dtppn(2,1,1,1,2)
ptppn(2,1,1,1,2)
qtppn(0.5,1,1,1,2)
rtppn(10,1,1,1,2)
```


